\bfseries Don't interpolate your data!

### 2022-10-16 main.tex
tweaks

\section{Introduction}

Things to emphasize here and below:
\begin{itemize}
\item The input--output relationship of this modeling approach is identical to the input--output relationship of the shift-and-coadd approach. It is just better.
\item People have a lot of hangups about the word ``model''. We have to use another word, or be very very careful how we use this word. For instance, some people I talked to about this thought I meant a physical model of the spectrum starting with atomic physics!
\item We have to explain why and how we are better than other approaches in terms that people care about (like radial-velocity precision and abundances etc).
\item All this is even more important in ill-sampled contexts than well-sampled contexts. See, for example, \textsl{APOGEE} raw data!
\item We should choose a rigid terminology and stick to it here. HOGG is currently liking ``combined spectrum'' for the model expectation.
\end{itemize}

\section{Concepts and assumptions}

@@

\section{Method}

@@

\section{Experiments and results}

@@

We show the results of this combintation, for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??

@@

The combined spectrum resulting from the method for forward modeling described in \sectionname~\ref{sec:method} is shown in \figurename~\ref{fig:combined}.
Again, it is compared to the true spectral expectation model.
We find HOGG WHAT?? HERE SAY ABSOLUTELY WHAT WE FIND.

HOGG: HERE SAY WHAT WE FIND RELATIVELY to the standard practice.

\section{Discussion}

>>>>

\section{Introduction}\label{sec:intro}

Things to emphasize here and below:
\begin{itemize}
\item The input--output relationship of this modeling approach is identical to the input--output relationship of the shift-and-coadd approach. It is just better.
\item People have a lot of hangups about the word ``model''. We have to use another word, or be very very careful how we use this word. For instance, some people I talked to about this thought I meant a physical model of the spectrum starting with atomic physics!
\item We have to explain why and how we are better than other approaches in terms that people care about (like radial-velocity precision and abundances etc).
\item All this is even more important in ill-sampled contexts than well-sampled contexts. See, for example, \textsl{APOGEE} raw data!
\item We should choose a rigid terminology and stick to it here. HOGG is currently liking ``combined spectrum'' for the model expectation.
\item This model is a sub-model of \textsl{wobble} \cite{wobble}.
\end{itemize}

\section{Concepts and assumptions}\label{sec:assumptions}

@@

\section{Method}\label{sec:method}

@@

\section{Experiments and results}\label{sec:results}

@@

We show the results of Standar Practice (tm), for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??

@@

The combined spectrum resulting from the Forward Model (tm) described in \sectionname~\ref{sec:method} is shown in \figurename~\ref{fig:combined}.
Again, it is compared to the true spectral expectation model.
We find HOGG WHAT?? HERE SAY ABSOLUTELY WHAT WE FIND.

HOGG: HERE SAY WHAT WE FIND RELATIVELY to Standard Practice (tm).

\section{Discussion}\label{sec:discussion}
